Calculating life expectancy and exploring missingness

### 2016-11-04 Code/1_Explore_Data_v2.Rmd
small cleanup

  list.life.tables[[list.index]] <- life.table(data = subset(dat2, StateYearRaceSex == stratum.id), 
                                               age.groups = "Age2", num.ages.in.group = "nx", 
                                               death.counts = "total_deaths5", 
                                               population.counts = "Population")
  list.index <- list.index + 1
  }
)

>>>>

  list.life.tables[[list.index]] <- life.table(data = subset(dat2, StateYearRaceSex == stratum.id), 
                                               num.ages.in.group = "nx", 
                                               death.counts = "total_deaths5", 
                                               population.counts = "Population")
  list.index <- list.index + 1
  }
)
